GSE158420: RNA expression downsampling

### 2024-09-14 analysis/docker_results/GSE158420_rna.Rmd
ylim

### PDF CHART
pdf("sens_vio.pdf",height=4,width=8)
par(mfrow=c(1,3))
vioplot(lapply(fores,function(mx) { mx[,2] } ) , side="left" , col="white" , border = "red",
  plotCentre = "line", ylim=c(0,457), xlab="Sample size", ylab="no. pathways")
  mtext("no. consistent pathways FDR<0.05" ,cex=0.8)
vioplot(lapply(fgres,function(mx) { mx[,2] } ) , side="right" , col="white", border="blue" ,
   add = TRUE, plotCentre = "line")

>>>>

### PDF CHART
pdf("sens_vio.pdf",height=4,width=8)
par(mfrow=c(1,3))
vioplot(lapply(fores,function(mx) { mx[,2] } ) , side="left" , col="white" , border = "red",
  plotCentre = "line", ylim=c(0,length(fsets)), xlab="Sample size", ylab="no. pathways")
  mtext("no. consistent pathways FDR<0.05" ,cex=0.8)
vioplot(lapply(fgres,function(mx) { mx[,2] } ) , side="right" , col="white", border="blue" ,
   add = TRUE, plotCentre = "line")
